Intelligence and Age at First Intercourse: Cause or Confound?

### 2015-08-05 afidraftRnw.Rnw
update

library(devtools);dev_mode(on=T)
#install_github("LiveOak/NlsyLinks")
#install_github("ggplot2")#dev_mode(on=F) 
#install_github("harrelfe/Hmisc")
library(knitr)
library(ggplot2)
library(effects)
library(stargazer)
library(NlsyLinks)
library(plyr)
library(tables)
library(Hmisc)
library(MplusAutomation)
library(WrightMap)
#Functions
####### FUNCTIONS #######
source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")

@@

#Data_9
LinkedMDAN_discord_AFI_z_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_910811.csv",sep=""))
LinkedMDAN_discord_AFI_z_9$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_9$Gendermean)
LinkedMDAN_discord_AFI_g_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_910811.csv",sep=""))
LinkedMDAN_discord_AFI_b_9 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_910811.csv",sep=""))

@@

model.meankids.g_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_9<-anova(model.diffkids.g.nested_9,model.diffkids.g.full_9)
model.diffmoms.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_9
model.meankids.b_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_10
LinkedMDAN_discord_AFI_z_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_z_10$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_10$Gendermean)
LinkedMDAN_discord_AFI_g_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_b_10 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_1011912.csv",sep=""))

@@

model.meankids.g_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_10<-anova(model.diffkids.g.nested_10,model.diffkids.g.full_10)
model.diffmoms.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_10
model.meankids.b_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_11
LinkedMDAN_discord_AFI_z_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_z_11$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_11$Gendermean)
LinkedMDAN_discord_AFI_g_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_b_11 <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_11121013.csv",sep=""))
data=LinkedMDAN_discord_AFI_z_11

@@

model.meankids.g_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_11<-anova(model.diffkids.g.nested_11,model.diffkids.g.full_11)
model.diffmoms.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_11
model.meankids.b_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#summarystats
birthweight <- read.table(paste(file_drive,"/Dropbox/SAS/MyFolders/79/SASGen1Kids/birthweight.dat",sep=""), quote="\"", stringsAsFactors=FALSE)
names(birthweight)<-c('CASEID','MCASEID','RACE','SEX_G2','YRB','WGT')
birthweight$WGT[birthweight$WGT < 0] <- NA
birthweight$firstborn<-0
birthweight$firstborn<-substrRight(birthweight$CASEID,2)
birthweight_2<-birthweight
birthweight$born[birthweight$firstborn!="01"]<-0
birthweight$born[birthweight$firstborn=="01"]<-1
birthweight_fb <- birthweight[ which(birthweight$born==1), ]

@@

momintel <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/79/SASGen1/momintel.csv",sep=""), header=FALSE)
names(momintel)<-c("MCASEID","Intel_G1","Intel_G1_SE","HID")
#momintel$zIntel_G1<-scale(momintel$Intel_G1, center = TRUE, scale = TRUE)*15+100

kidintel<-read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(kidintel)<-c("CASEID","ASEID","Intel_G2","Intel_G2_SE","MCASEID")
#kidintel$zIntel_G2<-scale(kidintel$Intel_G2, center = TRUE, scale = TRUE)*15+100
Gen1AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/CTT/Gen1AFI_exportconcor_910811.csv",sep=""))
Gen1AFI_exportconcor <- Gen1AFI_exportconcor[2:length(Gen1AFI_exportconcor[,1]),]
names(Gen1AFI_exportconcor)<-c("MCASEID","AFI_G1")
Gen2AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/SAS/MyFolders/NLSYSAS/Gen2AFI_exportconcor_910811.csv",sep=""))
names(Gen2AFI_exportconcor)<-c("CASEID","AFI_G2")

>>>>

library(devtools);dev_mode(on=T)
library(WrightMap)
library(knitr)
library(ggplot2)
library(effects)
library(stargazer)
library(NlsyLinks)
library(plyr)
library(tables)
library(Hmisc)
library(MplusAutomation)
#install_github("LiveOak/NlsyLinks")
#install_github("ggplot2")#dev_mode(on=F) 
#install_github("harrelfe/Hmisc")
#Functions
####### FUNCTIONS #######
source("https://raw.githubusercontent.com/smasongarrison/Functions/master/Mason_Functions.R")

@@

#Data_9
LinkedMDAN_discord_AFI_z_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_910811.csv",sep=""))
LinkedMDAN_discord_AFI_z_9$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_9$Gendermean)
LinkedMDAN_discord_AFI_g_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_910811.csv",sep=""))
LinkedMDAN_discord_AFI_b_9 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_910811.csv",sep=""))

@@

model.meankids.g_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_9<-anova(model.diffkids.g.nested_9,model.diffkids.g.full_9)
model.diffmoms.g_9<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_9
model.meankids.b_9<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_9<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_9<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_9 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_10
LinkedMDAN_discord_AFI_z_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_z_10$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_10$Gendermean)
LinkedMDAN_discord_AFI_g_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_1011912.csv",sep=""))
LinkedMDAN_discord_AFI_b_10 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_1011912.csv",sep=""))

@@

model.meankids.g_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_10<-anova(model.diffkids.g.nested_10,model.diffkids.g.full_10)
model.diffmoms.g_10<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_10
model.meankids.b_10<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_10<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_10<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_10 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#Data_11
LinkedMDAN_discord_AFI_z_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_z_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_z_11$Gendermean<-as.factor(LinkedMDAN_discord_AFI_z_11$Gendermean)
LinkedMDAN_discord_AFI_g_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_girls_11121013.csv",sep=""))
LinkedMDAN_discord_AFI_b_11 <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/LinkedMDAN_discord_AFI_boys_11121013.csv",sep=""))
data=LinkedMDAN_discord_AFI_z_11

@@

model.meankids.g_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.g_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
nested<-data
nested$Int_Mean[is.na(nested$Intdiff)] <- NA
model.diffkids.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffkids.g.full_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = nested)
model.diffkids.g.nested_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean , data = nested)
anova_11<-anova(model.diffkids.g.nested_11,model.diffkids.g.full_11)
model.diffmoms.g_11<- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.g_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
model.meanmomskids.g_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
data=LinkedMDAN_discord_AFI_b_11
model.meankids.b_11<-lm(AFIKIDmean ~ Int_Mean, data = data)
model.meanmoms.b_11<-lm(AFIKIDmean ~ INTMOMmean, data = data)
model.meanmomskids.b_11<-lm(AFIKIDmean ~ INTMOMmean + Int_Mean, data = data)
model.diffkids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + Int_Mean + Intdiff, data = data)
model.diffmoms.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean + INTMOMmean + INTMOMdiff, data = data)
model.diffmomskids.b_11 <- lm(AFIKIDdiff ~ AFIKIDmean +Int_Mean + Intdiff+ INTMOMmean + INTMOMdiff, data = data)
#summarystats
birthweight <- read.table(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/SASGen1Kids/birthweight.dat",sep=""), quote="\"", stringsAsFactors=FALSE)
names(birthweight)<-c('CASEID','MCASEID','RACE','SEX_G2','YRB','WGT')
birthweight$WGT[birthweight$WGT < 0] <- NA
birthweight$firstborn<-0
birthweight$firstborn<-substrRight(birthweight$CASEID,2)
birthweight_2<-birthweight
birthweight$born[birthweight$firstborn!="01"]<-0
birthweight$born[birthweight$firstborn=="01"]<-1
birthweight_fb <- birthweight[ which(birthweight$born==1), ]

@@

momintel <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/SASGen1/momintel.csv",sep=""), header=FALSE)
names(momintel)<-c("MCASEID","Intel_G1","Intel_G1_SE","HID")
#momintel$zIntel_G1<-scale(momintel$Intel_G1, center = TRUE, scale = TRUE)*15+100

kidintel<-read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/79/kidsintl/cleaned_CFA_G_around_910811.csv",sep=""), header=FALSE)
names(kidintel)<-c("CASEID","ASEID","Intel_G2","Intel_G2_SE","MCASEID")
#kidintel$zIntel_G2<-scale(kidintel$Intel_G2, center = TRUE, scale = TRUE)*15+100
Gen1AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/CTT/Gen1AFI_exportconcor_910811.csv",sep=""))
Gen1AFI_exportconcor <- Gen1AFI_exportconcor[2:length(Gen1AFI_exportconcor[,1]),]
names(Gen1AFI_exportconcor)<-c("MCASEID","AFI_G1")
Gen2AFI_exportconcor <- read.csv(paste(file_drive,"/Dropbox/Software/SAS/MyFolders/NLSYSAS/Gen2AFI_exportconcor_910811.csv",sep=""))
names(Gen2AFI_exportconcor)<-c("CASEID","AFI_G2")
